---
title: "p8105_hw1_fm2751"
output: github_document
date: "2022-09-22"
---
# Problem 0.1
Public GitHub repo, local R Project, and .Rmd file created and rendered to github_document.

# Problem 0.2
See below.

# Problem 1
First, I install the package "palmerpenguins" in the console and load library for later use.

```{r}
library(tidyverse)
```

Second, I load the dataset "penguins".
```{r Load}
data("penguins", package = "palmerpenguins")
```
## Description of the penguins dataset
In this section, you can have a summary about the "penguins" dataset. Also, you can view the first 5 rows of the dataset to get a general idea.
```{r Summary}
summary(penguins)
head(penguins, 5)
nrow(penguins)
ncol(penguins)
```
The "penguins" dataset consists of 344 observations and 8 variables (which are species, island, bill length in mm, bill depth in mm, flipper length in mm, body mass in g, sex and year of birth). The "penguins" dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. This study collected data from 3 species of penguins (Adelie, Chinstrap, and Gentoo) found on 3 different islands (Biscoe, Dream, and Torgersen). Among all variables, the diversity in penguins' body mass is the greatest, ranging from `r min(penguins$body_mass_g, na.rm = TRUE)`g to `r max(penguins$body_mass_g, na.rm = TRUE)`g. The number of female penguins (165) and male penguins (168) are similar to each other. Penguins has a mean flipper length of `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)`mm.

## Plots
In this section, you will see a scatterplot illustrating the association between penguins' flipper length and bill length.

```{r Plot}
flipper_bill <- ggplot(data = penguins,
                         aes(x = bill_length_mm,
                             y = flipper_length_mm)) +
  geom_point(aes(color = species, 
                 shape = species),
             size = 3,
             alpha = 0.8) +
  scale_color_manual(values = c("pink","purple","blue")) +
  labs(title = "Flipper length vs. bill length",
       x = "Bill length (mm)",
       y = "Flipper length (mm)",
       color = "Penguin species",
       shape = "Penguin species") +
  theme(legend.position = c(0.85, 0.15),
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position = "plot")
flipper_bill
ggsave("flipper_bill.pdf", height = 4, width = 6)
```
* NOTE: I have checked that flipper_bill.pdf has been successfully saved in my project directory.

# Problem 2
In this section, I will create a data frame comprised of
* a random sample of size 10 from a standard Normal distribution;
* a logical vector indicating whether elements of the sample are greater than 0;
* a character vector of length 10;
* a factor vector of length 10, with 3 different factor “levels”.

```{r Dataframe}
df = tibble(
  sample = rnorm(10),
  vec_logic = sample > 0,
  vec_char = c("b", "e", "a", "u", "u", "t", "i", "f", "u", "l"),
  vec_factor = factor(c("Low", "Medium", "High", "Low", "High", "Medium", "High", "Low", "Medium", "High"))
)
df
mean(df$sample)
mean(df$vec_logic)
mean(df$vec_char)
mean(df$vec_factor)
```

```{r, echo=TRUE, results='hide'}
mean(as.numeric(df$sample))
mean(as.numeric(df$vec_logic))
mean(as.numeric(df$vec_char))
mean(as.numeric(df$vec_factor))
```
Explanation:

